### 2023-04-12 resilience-safe-down.tex
up

As an example, let us choose $\Safe=S-\Bad$ then since $\Bad=\uparrow \Bad$, we have: $\Safe=\downarrow \Safe$.
%
\alain{definir  ideal-effective WSTS}
%
\begin{theorem}\label{up-down}
The resilience problem is decidable for ideal-effective WSTS with 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
the additional hypothesis that
for all downward-closed set $D \subseteq S$, the set $\pred^*(D)$ is downward-closed.
% \alain{est-ce que  $\pred(D)$ is downward closed avec D downward closed serait suffisant ? si l'ordre est omega2 alors closbas+inclusion est wqo donc il faudrait juste que la suite croissante $pred^n(D)+le reste$ converge...}
\end{theorem}

@@

\alain{à quoi ça sert ici ?: quelle signification ?Decidability of $U$ and $\Safe$ imply the decidability of $\Bad$.}
\mathieu{Pas convaincu que ça serve, je vais enlever}

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WSTS with strong %upward-
compatibility, then $\pred^{\leq n}(\Safe)= \uparrow~\pred^{\leq n}(\Safe)$ for all $n \in \N$,\alain{$\pred^n$ ou $\pred^{\leq n}$ ? même question pour post. et où est-ce défini ?}
and there exists $n_0 \in \N$ such that 
$\pred^{\leq n_0}(\Safe) = \uparrow \pred^{\leq n_0}(\Safe) = \uparrow \pred^*(\Safe) = \pred^*(\Safe)$.
Hence the equivalence.
\end{proof}

>>>>

As an example, let us choose $\Safe=S-\Bad$ then since $\Bad=\uparrow \Bad$, we have: $\Safe=\downarrow \Safe$.
%
% \alain{definir  ideal-effective WSTS}
%
\begin{theorem}\label{up-down}
The resilience problem is decidable for ideal-effective WSTS with 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
the additional hypothesis that
for all downward-closed set $D \subseteq S$, the set $\pred^*(D)$ is downward-closed.
% \alain{est-ce que  $\pred(D)$ is downward closed avec D downward closed serait suffisant ? si l'ordre est omega2 alors closbas+inclusion est wqo donc il faudrait juste que la suite croissante $pred^n(D)+le reste$ converge...}
\end{theorem}

@@

\iffalse
\alain{à quoi ça sert ici ?: quelle signification ?Decidability of $U$ and $\Safe$ imply the decidability of $\Bad$.}
\mathieu{Pas convaincu que ça serve, je vais enlever}
% hop
\fi

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WSTS with strong %upward-
compatibility, then $\pred^{\leq n}(\Safe)= \uparrow~\pred^{\leq n}(\Safe)$ for all $n \in \N$,
% \alain{$\pred^n$ ou $\pred^{\leq n}$ ? même question pour post. et où est-ce défini ?}
and there exists $n_0 \in \N$ such that 
$\pred^{\leq n_0}(\Safe) = \uparrow \pred^{\leq n_0}(\Safe) = \uparrow \pred^*(\Safe) = \pred^*(\Safe)$.
Hence the equivalence.
\end{proof}
